\chapter{Companion Calculators}\label{ch:calculators}

Every formula in this book has a companion interactive calculator at
\href{https://rftoolbox.ca}{rftoolbox.ca} --- enter your own numbers and read the
answer, with the same diagrams used here. The tools are listed below by category,
each cross-referenced to the chapter of this book that develops its theory. All are
free and run in the browser.

\section*{Fundamentals \& EM}
\addcontentsline{toc}{section}{Fundamentals \& EM}
\noindent\emph{See Chapter~1 (Electromagnetic Foundations).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Wavelength.html}{\textbf{Wavelength}} & Free-space λ from frequency and dielectric constant. \\
\href{https://rftoolbox.ca/FreqEnergyConverter.html}{\textbf{Freq / λ / Energy}} & Live converter: frequency, wavelength, period, photon energy, B₀. \\
\href{https://rftoolbox.ca/SkinDepth.html}{\textbf{Skin Depth}} & Conductor skin depth vs frequency and conductivity. \\
\href{https://rftoolbox.ca/dBmConverter.html}{\textbf{dBm ↔ Watts}} & Convert between dBm and watts in either direction. \\
\href{https://rftoolbox.ca/PlaneWave.html}{\textbf{Plane Wave / Power Density}} & Wave impedance, E/H fields and power density (Poynting) for a plane wave. \\
\href{https://rftoolbox.ca/FieldStrength.html}{\textbf{Field Strength Converter}} & V/m ↔ dBµV/m ↔ A/m ↔ W/m², or field from EIRP and distance. \\
\href{https://rftoolbox.ca/DielectricBoundary.html}{\textbf{Dielectric Boundary (Fresnel)}} & Reflection/transmission vs angle, Brewster and critical angles at an interface. \\
\href{https://rftoolbox.ca/LossTangent.html}{\textbf{Dielectric Loss Tangent}} & Complex permittivity, dielectric Q, attenuation and wavelength in a material. \\
\href{https://rftoolbox.ca/ThermalNoise.html}{\textbf{Thermal (kTB) Noise}} & Johnson–Nyquist noise voltage/current and available noise power kTB. \\
\href{https://rftoolbox.ca/ShieldingEffectiveness.html}{\textbf{Shielding Effectiveness}} & Absorption + reflection loss and total SE of a metal barrier (far-field plane wave). \\
\href{https://rftoolbox.ca/KittelResonance.html}{\textbf{Ferrite Resonance}} & Gyromagnetic (Kittel) resonance and the Polder permeability tensor μ, κ of a biased ferrite. \\
\hline
\end{longtable}

\section*{Resonance \& Passives}
\addcontentsline{toc}{section}{Resonance \& Passives}
\noindent\emph{See Chapter~4 (Passive Components, Resonators and Filters).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/LC.html}{\textbf{LC Circuit Solver}} & Solve for L, C, or f₀ — fill any two, get the third. \\
\href{https://rftoolbox.ca/CLC.html}{\textbf{LC Tuning Capacitor}} & Capacitance needed to resonate a given inductor at a target frequency. \\
\href{https://rftoolbox.ca/CoupledResonators.html}{\textbf{Coupled Resonators}} & Mode splitting, bandwidth, and coupling regime for two magnetically coupled LC tanks. \\
\href{https://rftoolbox.ca/BandpassCalc.html}{\textbf{Bandpass Calculator}} & f₀, Q, and bandwidth from R, L, C for series or parallel RLC. \\
\href{https://rftoolbox.ca/Solenoid.html}{\textbf{Solenoid Inductance}} & Inductance of a single-layer air-core or cored coil (Wheeler's formula) from turns, diameter, and length. \\
\href{https://rftoolbox.ca/Varactor.html}{\textbf{Varactor C–V Tuning}} & Varactor capacitance vs bias, tuning ratio, and resonant-frequency tuning range. \\
\href{https://rftoolbox.ca/ParallelPlateCap.html}{\textbf{Parallel-Plate Capacitor}} & Capacitance from plate area, gap, dielectric and plate count, plus field and stored energy. \\
\href{https://rftoolbox.ca/BondWire.html}{\textbf{Bond Wire Inductance}} & Parasitic inductance and reactance of a bond wire (Grover formula). \\
\href{https://rftoolbox.ca/WireInductance.html}{\textbf{Wire Inductance}} & Self-inductance of a straight wire, circular loop, or two-wire line. \\
\href{https://rftoolbox.ca/ToroidInductor.html}{\textbf{Toroid Inductor}} & Turns from the core AL value and target inductance (L = AL·N²), plus a flux-density check. \\
\href{https://rftoolbox.ca/CapacitorSRF.html}{\textbf{Capacitor SRF}} & Self-resonant frequency from C and parasitic ESL, plus Q and reactance at frequency. \\
\href{https://rftoolbox.ca/ResonatorQ.html}{\textbf{Resonator Q}} & Loaded/unloaded/external Q, 3-dB bandwidth, coupling and insertion loss. \\
\href{https://rftoolbox.ca/FerriteBead.html}{\textbf{Ferrite Bead / Choke}} & Approximate bead impedance from a series R–L model or a datasheet point. \\
\hline
\end{longtable}

\section*{Transmission Lines}
\addcontentsline{toc}{section}{Transmission Lines}
\noindent\emph{See Chapters~2--3 (Transmission Lines; Guided-Wave Structures).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Microstrip.html}{\textbf{Microstrip}} & Z₀ and εeff from geometry, or trace width from target Z₀. \\
\href{https://rftoolbox.ca/Coaxial.html}{\textbf{Coaxial Line}} & Z₀, velocity factor, and cutoff frequency for coax cable. \\
\href{https://rftoolbox.ca/Stripline.html}{\textbf{Stripline}} & Fully shielded TEM stripline between two ground planes. \\
\href{https://rftoolbox.ca/CPW.html}{\textbf{Coplanar Waveguide}} & CPW and GCPW Z₀ using elliptic integral conformal mapping. \\
\href{https://rftoolbox.ca/DiffPair.html}{\textbf{Differential Pair}} & Z\_diff and Z\_odd for edge-coupled microstrip pairs. \\
\href{https://rftoolbox.ca/StubCalc.html}{\textbf{Stub Calculator}} & Open/short stub length for a target shunt susceptance. \\
\href{https://rftoolbox.ca/QuarterWave.html}{\textbf{Quarter-Wave Transformer}} & λ/4 impedance transformer Z and physical length. \\
\href{https://rftoolbox.ca/TLLoss.html}{\textbf{TL Loss \& Delay}} & Conductor + dielectric insertion loss and propagation delay for microstrip and coax. \\
\href{https://rftoolbox.ca/TDR.html}{\textbf{TDR Fault Distance}} & Locate a cable fault from the echo delay and velocity factor, plus the fault impedance. \\
\href{https://rftoolbox.ca/PCBVia.html}{\textbf{PCB Via Parasitics}} & Via inductance, antipad capacitance, and self-resonant frequency. \\
\href{https://rftoolbox.ca/CoaxPowerHandling.html}{\textbf{Coax Power Handling}} & Peak voltage-breakdown power and Z₀ of a coaxial line from geometry and dielectric. \\
\href{https://rftoolbox.ca/TLResonator.html}{\textbf{Transmission-Line Resonator}} & λ/2 and λ/4 open/short line resonators: length, unloaded Q from attenuation, equivalent RLC. \\
\hline
\end{longtable}

\section*{Matching \& Dividers}
\addcontentsline{toc}{section}{Matching \& Dividers}
\noindent\emph{See Chapter~2 (Transmission Lines and Impedance).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/SmithChart.html}{\textbf{Interactive Smith Chart}} & HiDPI Smith Chart — click to read, pin points, rotate with stubs. \\
\href{https://rftoolbox.ca/VSWRConverter.html}{\textbf{VSWR / Return Loss}} & Live converter between VSWR, |Γ|, return loss, and mismatch loss. \\
\href{https://rftoolbox.ca/LNetwork.html}{\textbf{L-Network Matcher}} & L, C values for single-frequency impedance matching. \\
\href{https://rftoolbox.ca/PiTNetwork.html}{\textbf{Pi / T Network}} & Pi and T matching networks with free choice of loaded Q. \\
\href{https://rftoolbox.ca/ImpedanceMatchingNetwork.html}{\textbf{Impedance Matching Network}} & L-network for complex Z<sub>S</sub> Z<sub>L</sub> with Smith Chart trajectories. \\
\href{https://rftoolbox.ca/CapacitorNetwork.html}{\textbf{Capacitor Network}} & Total capacitance for series and parallel combinations. \\
\href{https://rftoolbox.ca/LCBalun.html}{\textbf{LC BALUN}} & Lattice and Pi BALUN design with impedance transformation. \\
\href{https://rftoolbox.ca/Wilkinson.html}{\textbf{Wilkinson Divider}} & Equal and unequal power splits with isolation resistor. \\
\href{https://rftoolbox.ca/Coupler.html}{\textbf{Coupler \& Hybrid}} & Coupled-line, branchline (90°), and rat-race (180°) hybrid design. \\
\href{https://rftoolbox.ca/PowerCombiner.html}{\textbf{Power Combining}} & N-way combiner output power with efficiency and failure analysis. \\
\href{https://rftoolbox.ca/PhaseShifter.html}{\textbf{Digital Phase Shifter}} & LSB step, number of states, and RMS quantization error of an N-bit phase shifter. \\
\href{https://rftoolbox.ca/MismatchLoss.html}{\textbf{Mismatch Loss}} & Mismatch loss, return loss, VSWR, |Γ| and reflected/transmitted power. \\
\href{https://rftoolbox.ca/SingleStubMatch.html}{\textbf{Single-Stub Matching}} & Shunt-stub position and open/short length to match a complex load (both solutions). \\
\href{https://rftoolbox.ca/DoubleStubTuner.html}{\textbf{Double-Stub Tuner}} & Two-stub matching for a fixed spacing, both solutions, with the forbidden-region check. \\
\href{https://rftoolbox.ca/MultisectionTransformer.html}{\textbf{Multisection λ/4 Transformer}} & Binomial or Chebyshev multisection transformer: section impedances and bandwidth. \\
\href{https://rftoolbox.ca/KlopfensteinTaper.html}{\textbf{Tapered-Line Matching}} & Exponential, triangular and Klopfenstein taper reflection response and cutoff. \\
\href{https://rftoolbox.ca/BodeFano.html}{\textbf{Bode–Fano Limit}} & Theoretical best matching bandwidth (or minimum reflection) for a reactive load. \\
\hline
\end{longtable}

\section*{Filters \& Attenuators}
\addcontentsline{toc}{section}{Filters \& Attenuators}
\noindent\emph{See Chapter~4 (Passive Components, Resonators and Filters).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/RCFilter.html}{\textbf{First-Order Filter}} & RC \& RL low-pass / high-pass: cutoff frequency, τ, and roll-off. \\
\href{https://rftoolbox.ca/FilterDesign.html}{\textbf{LC Filter Designer}} & Butterworth/Chebyshev LP/HP up to 9th order with BOM. \\
\href{https://rftoolbox.ca/AttenuatorDesign.html}{\textbf{Attenuator Designer}} & Pi, T, L-pad, and Bridged-T resistor values for any attenuation. \\
\href{https://rftoolbox.ca/SteppedImpedanceLPF.html}{\textbf{Stepped-Z LPF}} & Microstrip stepped-impedance LPF: Butterworth or Chebyshev, with trace dimensions. \\
\href{https://rftoolbox.ca/GroupDelay.html}{\textbf{Filter Group Delay}} & Band-center group delay of a Butterworth or Chebyshev lowpass prototype from its poles. \\
\href{https://rftoolbox.ca/FilterPrototype.html}{\textbf{Filter Prototype g-Values}} & Butterworth \& Chebyshev lowpass g-values of any order, plus denormalised L/C. \\
\href{https://rftoolbox.ca/CoupledLineFilter.html}{\textbf{Coupled-Line Filter}} & Parallel coupled-line bandpass: J-inverters and even/odd-mode impedances per section. \\
\href{https://rftoolbox.ca/StubFilter.html}{\textbf{Stub Filter (Richards)}} & λ/8 short- and open-circuit stub impedances from a lumped lowpass prototype. \\
\hline
\end{longtable}

\section*{Amplifiers \& Devices}
\addcontentsline{toc}{section}{Amplifiers \& Devices}
\noindent\emph{See Chapters~5--6 (Active Devices; Signal Generation).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/NoiseFigure.html}{\textbf{Cascaded Noise Figure}} & System NF and gain for up to 8 cascaded stages (Friis). \\
\href{https://rftoolbox.ca/AmpStability.html}{\textbf{Amplifier Stability}} & Rollett K-factor, µ-factor, MAG/MSG from S-parameters. Unconditional stability check. \\
\href{https://rftoolbox.ca/IP3Calc.html}{\textbf{IP3 \& Intermodulation}} & OIP3, IM3 product power, and IMD ratio from IIP3 and gain. \\
\href{https://rftoolbox.ca/TransistorFT.html}{\textbf{Transistor fT / fmax}} & Transition and maximum oscillation frequency from gm, capacitances and gate resistance. \\
\href{https://rftoolbox.ca/TransducerGain.html}{\textbf{Unilateral Transducer Gain}} & Maximum gain from S-parameter magnitudes, with source and load match contributions. \\
\href{https://rftoolbox.ca/LNAMatch.html}{\textbf{LNA Noise Match}} & Noise figure for any source reflection from the noise parameters Fmin, Rn and Γopt. \\
\href{https://rftoolbox.ca/NFYFactor.html}{\textbf{Noise Figure (Y-Factor)}} & Noise figure and noise temperature from the Y-factor measurement and source ENR. \\
\href{https://rftoolbox.ca/PLLFilter.html}{\textbf{PLL Loop Filter}} & Type-2 3rd-order passive loop filter component values from bandwidth and phase margin. \\
\href{https://rftoolbox.ca/PhaseNoiseJitter.html}{\textbf{Phase Noise   Jitter}} & Integrate a piecewise phase noise profile to RMS jitter. \\
\href{https://rftoolbox.ca/DDS.html}{\textbf{DDS Frequency}} & Output frequency, tuning word and resolution of a direct digital synthesizer. \\
\href{https://rftoolbox.ca/NoiseTempNF.html}{\textbf{Noise Temp ↔ NF}} & Convert noise figure (dB) ↔ noise factor ↔ equivalent noise temperature (K), plus added noise power. \\
\href{https://rftoolbox.ca/LeesonPhaseNoise.html}{\textbf{Leeson Phase Noise}} & Predict oscillator L(fm) from loaded Q, noise figure, power and flicker corner. \\
\href{https://rftoolbox.ca/PALoadLine.html}{\textbf{PA Load-Line (Cripps)}} & Optimum load, maximum output power and drain efficiency for an RF power amplifier. \\
\href{https://rftoolbox.ca/JunctionTemp.html}{\textbf{Junction Temperature}} & Device junction temperature and margin from the θjc/θcs/θsa thermal chain. \\
\href{https://rftoolbox.ca/CrystalResonator.html}{\textbf{Quartz Crystal Resonator}} & Series/parallel resonance, Q, capacitance ratio and pullability from motional L1/C1/R1/C0. \\
\href{https://rftoolbox.ca/AmpDesignCircles.html}{\textbf{Amplifier Design Circles}} & Stability, available-gain and noise-figure circles on the source-plane Smith chart from S-parameters. \\
\href{https://rftoolbox.ca/ConjugateMatch.html}{\textbf{Simultaneous Conjugate Match}} & Source/load reflections and maximum transducer gain for a bilateral amplifier. \\
\href{https://rftoolbox.ca/NegResOscillator.html}{\textbf{Neg-Resistance Oscillator}} & One-port oscillator load design: Z\_L = −Z\_in, reflection condition and start-up margin. \\
\href{https://rftoolbox.ca/PINDiodeSwitch.html}{\textbf{PIN Diode Switch}} & Series/shunt PIN diode SPST insertion loss and isolation from R\_f and C\_j. \\
\hline
\end{longtable}

\section*{Receivers \& DSP}
\addcontentsline{toc}{section}{Receivers \& DSP}
\noindent\emph{See Chapter~8 (RF Systems, Receivers and Communications).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Sensitivity.html}{\textbf{Receiver Sensitivity / MDS}} & Noise floor, minimum detectable signal, and spurious-free dynamic range from bandwidth, NF, SNR and IIP3. \\
\href{https://rftoolbox.ca/ImageReject.html}{\textbf{Image Frequency \& Rejection}} & Image and LO frequencies plus image-rejection ratio from I/Q gain and phase imbalance. \\
\href{https://rftoolbox.ca/ADCNoise.html}{\textbf{ADC SNR / ENOB}} & Quantization SNR, aperture-jitter-limited SNR, combined SNR and effective number of bits. \\
\href{https://rftoolbox.ca/EVMSNR.html}{\textbf{EVM ↔ SNR Converter}} & Convert error vector magnitude to/from SNR/MER, with the densest supportable QAM order. \\
\href{https://rftoolbox.ca/BandpassSampling.html}{\textbf{Bandpass Sampling}} & Nyquist zone, aliased IF, spectral inversion and minimum sample rate for undersampling. \\
\href{https://rftoolbox.ca/SpectrumDANL.html}{\textbf{Spectrum Analyzer DANL}} & Displayed average noise level and sensitivity from RBW, noise figure and attenuation. \\
\href{https://rftoolbox.ca/RFCascadeAnalyzer.html}{\textbf{RF Cascade Analyzer}} & Cumulative gain, cascaded noise figure, IIP3/IIP2, noise floor and SFDR for a multi-stage chain. \\
\href{https://rftoolbox.ca/MixerSpurChart.html}{\textbf{Mixer Spur Chart}} & m·LO ± n·RF spurious products landing in the IF band, plus image and half-IF frequencies. \\
\href{https://rftoolbox.ca/ModulationBandwidth.html}{\textbf{Modulation Bandwidth \& Eb/N0}} & Symbol rate, raised-cosine occupied bandwidth, spectral efficiency and Eb/N0 ↔ SNR. \\
\href{https://rftoolbox.ca/BERvsEbN0.html}{\textbf{BER vs Eb/N0}} & Bit error rate for BPSK/QPSK/M-PSK/M-QAM in AWGN, with the waterfall curve and required Eb/N0. \\
\href{https://rftoolbox.ca/OFDMParameters.html}{\textbf{OFDM Parameters}} & Symbol time, cyclic-prefix overhead, occupied bandwidth, PAPR bound and data rate. \\
\href{https://rftoolbox.ca/MixerConversionLoss.html}{\textbf{Mixer Conversion Loss}} & SSB/DSB mixer noise figure and cascaded receiver noise figure from conversion loss. \\
\href{https://rftoolbox.ca/SchottkyDetector.html}{\textbf{Schottky Detector}} & Detector responsivity, video resistance, NEP and tangential signal sensitivity. \\
\hline
\end{longtable}

\section*{Antennas \& Arrays}
\addcontentsline{toc}{section}{Antennas \& Arrays}
\noindent\emph{See Chapter~7 (Antennas and Propagation).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Dipole.html}{\textbf{Dipole Antenna}} & Half-wave dipole arm length and shortening factor. \\
\href{https://rftoolbox.ca/PatchAntenna.html}{\textbf{Patch Antenna}} & Patch width, length, and effective permittivity for any substrate. \\
\href{https://rftoolbox.ca/ArrayFactor.html}{\textbf{Array Factor Plotter}} & Polar radiation pattern for N-element linear arrays with steering. \\
\href{https://rftoolbox.ca/HelicalAntenna.html}{\textbf{Helical Antenna}} & Axial-mode helix gain, HPBW, and dimensions via Kraus formulas. \\
\href{https://rftoolbox.ca/YagiAntenna.html}{\textbf{Yagi-Uda Antenna}} & Gain, element lengths, and boom size for 2–9 element Yagis (NBS/Viezbicke tables). \\
\href{https://rftoolbox.ca/ApertureAntenna.html}{\textbf{Aperture Antenna Gain}} & Dish/horn gain from area and efficiency, plus the far-field (Fraunhofer) distance. \\
\href{https://rftoolbox.ca/ParabolicDish.html}{\textbf{Parabolic Dish}} & Reflector gain, half-power/first-null beamwidth and effective aperture from diameter. \\
\href{https://rftoolbox.ca/HornAntenna.html}{\textbf{Horn Antenna}} & Pyramidal/conical horn gain, effective aperture and beamwidth from the aperture size. \\
\href{https://rftoolbox.ca/AntennaGainConverter.html}{\textbf{Antenna Gain Converter}} & dBi ↔ dBd, EIRP, effective aperture (Gλ²/4π) and the far-field distance. \\
\href{https://rftoolbox.ca/MonopoleLoop.html}{\textbf{Monopole \& Small Loop}} & λ/4 monopole length/Rr/gain and small-loop radiation resistance and gain. \\
\hline
\end{longtable}

\section*{Propagation, Radar \& Links}
\addcontentsline{toc}{section}{Propagation, Radar \& Links}
\noindent\emph{See Chapter~8 (RF Systems, Receivers and Communications).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Friis.html}{\textbf{Friis Equation}} & Received power from EIRP, path loss, and antenna gains. \\
\href{https://rftoolbox.ca/LinkBudget.html}{\textbf{Link Budget}} & End-to-end RF link: EIRP, path loss, noise floor, SNR margin. \\
\href{https://rftoolbox.ca/FresnelZone.html}{\textbf{Fresnel Zone \& Clearance}} & First-zone radius and the 60\% clearance needed for a line-of-sight link. \\
\href{https://rftoolbox.ca/PathLoss.html}{\textbf{Path Loss Models}} & Free-space, two-ray, Okumura-Hata and COST-231 propagation loss. \\
\href{https://rftoolbox.ca/RadarRange.html}{\textbf{Radar Range Equation}} & R\_max and received power from transmit power, RCS, and gains. \\
\href{https://rftoolbox.ca/LinkCapacity.html}{\textbf{Shannon Capacity \& BER}} & Channel capacity, spectral efficiency, Eb/N0↔SNR and BPSK/QPSK bit error rate. \\
\href{https://rftoolbox.ca/ProcessingGain.html}{\textbf{Processing Gain \& Jamming Margin}} & Spread-spectrum processing gain from chip/data rate, plus jamming margin. \\
\href{https://rftoolbox.ca/Doppler.html}{\textbf{Doppler Shift}} & Doppler frequency shift for one-way links and two-way radar from speed and angle. \\
\href{https://rftoolbox.ca/GT.html}{\textbf{G/T Figure of Merit}} & Receive-system G/T and system noise temperature from gain, Tant and receiver NF. \\
\href{https://rftoolbox.ca/FMCWRadar.html}{\textbf{FMCW Radar}} & Range/velocity resolution, beat frequency and chirp slope for a frequency-modulated CW radar. \\
\href{https://rftoolbox.ca/RadarPRF.html}{\textbf{Radar PRF \& Ambiguity}} & Unambiguous range and velocity, blind speeds, PRI and duty cycle from the PRF. \\
\href{https://rftoolbox.ca/RCS.html}{\textbf{Radar Cross Section}} & RCS of a sphere, flat plate, cylinder or trihedral corner in m² and dBsm. \\
\hline
\end{longtable}

\section*{Waveguide}
\addcontentsline{toc}{section}{Waveguide}
\noindent\emph{See Chapter~3 (Guided-Wave Structures and Interconnect).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/Waveguide.html}{\textbf{Rectangular Waveguide}} & TE/TM mode cutoffs, guide wavelength, wave impedance, and conductor loss. \\
\href{https://rftoolbox.ca/CircularWaveguide.html}{\textbf{Circular Waveguide}} & TE/TM mode cutoffs using Bessel zeros, guide wavelength, wave impedance, and conductor loss. \\
\href{https://rftoolbox.ca/CavityResonator.html}{\textbf{Cavity Resonator}} & Rectangular/circular cavity resonant frequencies and the unloaded Q of the TE₁₀ℓ mode. \\
\href{https://rftoolbox.ca/DielectricResonator.html}{\textbf{Dielectric Resonator}} & Approximate TE01δ resonant frequency of a cylindrical dielectric puck. \\
\hline
\end{longtable}

\section*{MRI Coils \& Tools}
\addcontentsline{toc}{section}{MRI Coils \& Tools}
\noindent\emph{See Chapter~10 (MRI Physics and Coil Engineering).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/CLI.html}{\textbf{Loop Inductance}} & Inductance of a single circular loop (Rosa formula). \\
\href{https://rftoolbox.ca/CoilDesigner.html}{\textbf{Simple RF Coil Designer}} & Single-turn loop inductance L and the tuning capacitor C for resonance at f. \\
\href{https://rftoolbox.ca/SurfaceCoilDesigner.html}{\textbf{Advanced RF Coil Designer}} & Complete MRI surface receive coil design with matching network. \\
\href{https://rftoolbox.ca/BirdcageCoil.html}{\textbf{Birdcage Coil}} & LP/HP birdcage MRI volume coil: element values and mode frequencies. \\
\href{https://rftoolbox.ca/SAREstimator.html}{\textbf{SAR Estimator}} & Local SAR from B₁⁺, frequency, tissue type vs IEC limits. \\
\href{https://rftoolbox.ca/PhasedArrayDecoupling.html}{\textbf{Array Decoupling}} & Mutual inductance and overlap/capacitive/preamp decoupling. \\
\hline
\end{longtable}

\section*{Converters}
\addcontentsline{toc}{section}{Converters}
\noindent\emph{See Chapters~2 and~9 (Impedance; Measurement).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/TwoPortConverter.html}{\textbf{S/Z/Y/ABCD Converter}} & Convert between all four 2-port parameter representations. \\
\href{https://rftoolbox.ca/SParamPlotter.html}{\textbf{S-Parameter Plotter}} & Plot Touchstone .s1p–.s4p files with Chart.js. \\
\href{https://rftoolbox.ca/ESeries.html}{\textbf{E-Series Finder}} & Nearest standard R, C, or L value in E6–E192 with \% error. \\
\href{https://rftoolbox.ca/ABCDCascade.html}{\textbf{ABCD Matrix Cascade}} & Multiply two-port ABCD matrices (series Z, shunt Y, line, transformer) and convert to S-parameters. \\
\hline
\end{longtable}

\section*{Simulators}
\addcontentsline{toc}{section}{Simulators}
\noindent\emph{See Chapters~2--4 (Impedance; Components).}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\hline
\href{https://rftoolbox.ca/RFSimulator.html}{\textbf{RF Circuit Simulator}} & ABCD-matrix ladder network simulator: S-params, VSWR, group delay. \\
\href{https://rftoolbox.ca/SpiceSim.html}{\textbf{SPICE Simulator}} & MNA-based SPICE engine: .AC, .DC, .OP, .TRAN analyses in browser. \\
\hline
\end{longtable}

