\documentclass[11pt,openany]{book}
\input{preamble}
\graphicspath{{figures/}}

\begin{document}
\frontmatter

% ------------------------------------------------ title page
\begin{titlepage}
\centering
\vspace*{2.2cm}
{\color{rfpurple}\rule{\linewidth}{2pt}}\\[10pt]
{\sffamily\Huge\bfseries\color{rfpurple} RF \& Microwave Engineering}\\[10pt]
{\sffamily\LARGE An Interactive Textbook}\\[6pt]
{\sffamily\large with MRI Physics \& Coil Engineering}\\[8pt]
{\color{rfpurple}\rule{\linewidth}{2pt}}\\[26pt]
{\sffamily\large 15 Parts \quad\textbullet\quad 89 Chapters \quad\textbullet\quad 124 figures}\\[4pt]
{\sffamily\normalsize with companion interactive calculators}\\[3cm]
{\sffamily\Large\bfseries RF Toolbox}\\[4pt]
{\sffamily\normalsize\href{https://rftoolbox.ca}{rftoolbox.ca}}\\[1.2cm]
{\sffamily\small Compiled from the RF Toolbox reference library.}
\vfill
\end{titlepage}

% ------------------------------------------------ front matter
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
This book collects the RF Toolbox reference library — sixty-eight illustrated
articles on radio-frequency engineering, microwave design, and magnetic-resonance
imaging — into a single, sequenced volume, and extends it with further chapters on
active-device, receiver, communication-system, antenna, and test engineering. Each
reference topic began as a standalone web article at
\href{https://rftoolbox.ca}{rftoolbox.ca}; here they are re-ordered into a
foundations-to-advanced progression, grouped into fifteen Parts, and typeset with
their original diagrams.

The material spans classical electromagnetism, transmission-line theory and
impedance matching, guided-wave structures, passive components and filters, noise
and amplifier design, signal generation and frequency conversion, antennas,
complete RF systems, electromagnetic compatibility, and a full treatment of MRI
physics and RF coil engineering. Every chapter is paired online with an
interactive calculator that lets you put its equations to work with your own
numbers.

\chapter*{How to Use This Book}
\addcontentsline{toc}{chapter}{How to Use This Book}
The fifteen Parts are arranged so that each builds on the last, but chapters are also
written to stand alone for reference. If you are new to RF engineering, read Parts
I and II in order — waves, decibels, transmission lines, VSWR, the Smith chart, and
matching are the vocabulary everything else uses. Practitioners can jump directly to
the chapter they need.

Each chapter opens with \emph{Learning Objectives} and closes with a
\emph{Worked Example}, \emph{Key Takeaways}, and \emph{Exercises}; worked answers to
every exercise are collected in \emph{Solutions to Exercises} at the back, and each
chapter points to standard texts in the \emph{References}. Displayed equations are
boxed set-off results; symbols follow the conventions in the Notation section below. Wherever this book shows a formula, the online edition offers
a live calculator for it: for example, the VSWR / return-loss converter, the Smith
chart, the cascaded noise-figure and IP3 tools, the antenna calculators, and the MRI
coil and SAR estimators. Visit \href{https://rftoolbox.ca}{rftoolbox.ca} to use them.

\chapter*{Notation}
\addcontentsline{toc}{chapter}{Notation}
\begin{tabbing}
\hspace{3.2cm}\=\kill
$Z_0$ \> Characteristic impedance (ohms), typically 50 or 75~$\Omega$.\\
$\Gamma$ \> Voltage reflection coefficient, $\Gamma=(Z_L-Z_0)/(Z_L+Z_0)$.\\
VSWR \> Voltage standing-wave ratio, $(1+|\Gamma|)/(1-|\Gamma|)$.\\
$\lambda$ \> Wavelength; $\beta=2\pi/\lambda$ is the phase constant.\\
$f,\ \omega$ \> Frequency (Hz) and angular frequency $\omega=2\pi f$.\\
$S_{ij}$ \> Scattering parameters (S-parameters).\\
NF, $F$ \> Noise figure (dB) and noise factor (linear).\\
$B_0,\ B_1$ \> MRI static field and RF transmit field.\\
$\gamma$ \> Gyromagnetic ratio (MRI); also used for propagation constant in line theory.\\
\end{tabbing}
\noindent Decibel quantities: dBm is power referenced to 1~milliwatt; dBc is
relative to a carrier; dBi is antenna gain relative to an isotropic radiator.

\tableofcontents

% ------------------------------------------------ body
\mainmatter
\input{_book_body}

% ------------------------------------------------ back matter
\backmatter
\chapter{Solutions to Exercises}
The answers below are keyed to the end-of-chapter exercises. Try each problem
before checking here; many can be verified directly with the companion
calculator named in the chapter.
\input{_solutions}

\input{references}

\end{document}
