\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
\bibitem{pozar} D.~M. Pozar, \emph{Microwave Engineering}, 4th ed. Hoboken, NJ: Wiley, 2012.
\bibitem{collin} R.~E. Collin, \emph{Foundations for Microwave Engineering}, 2nd ed. New York: IEEE Press, 2001.
\bibitem{jackson} J.~D. Jackson, \emph{Classical Electrodynamics}, 3rd ed. New York: Wiley, 1998.
\bibitem{ramo} S. Ramo, J.~R. Whinnery, and T. Van Duzer, \emph{Fields and Waves in Communication Electronics}, 3rd ed. New York: Wiley, 1994.
\bibitem{steer} M. Steer, \emph{Microwave and RF Design}, 3rd ed. Raleigh, NC: NC State Univ., 2019.
\bibitem{ludwig} R. Ludwig and G. Bogdanov, \emph{RF Circuit Design: Theory and Applications}, 2nd ed. Upper Saddle River, NJ: Prentice Hall, 2009.
\bibitem{hayward} W. Hayward, \emph{Introduction to Radio Frequency Design}. Newington, CT: ARRL, 1994.
\bibitem{razavi} B. Razavi, \emph{RF Microelectronics}, 2nd ed. Upper Saddle River, NJ: Prentice Hall, 2011.
\bibitem{lee} T.~H. Lee, \emph{The Design of CMOS Radio-Frequency Integrated Circuits}, 2nd ed. Cambridge, U.K.: Cambridge Univ. Press, 2004.
\bibitem{gonzalez} G. Gonzalez, \emph{Microwave Transistor Amplifiers: Analysis and Design}, 2nd ed. Upper Saddle River, NJ: Prentice Hall, 1997.
\bibitem{cripps} S.~C. Cripps, \emph{RF Power Amplifiers for Wireless Communications}, 2nd ed. Norwood, MA: Artech House, 2006.
\bibitem{maas} S.~A. Maas, \emph{Microwave Mixers}, 2nd ed. Norwood, MA: Artech House, 1993.
\bibitem{rohde} U.~L. Rohde, \emph{Microwave and Wireless Synthesizers: Theory and Design}. New York: Wiley, 1997.
\bibitem{balanis} C.~A. Balanis, \emph{Antenna Theory: Analysis and Design}, 4th ed. Hoboken, NJ: Wiley, 2016.
\bibitem{kraus} J.~D. Kraus, \emph{Antennas}, 2nd ed. New York: McGraw-Hill, 1988.
\bibitem{viezbicke} P.~P. Viezbicke, ``Yagi antenna design,'' Nat. Bur. Stand., Tech. Note 688, 1976.
\bibitem{skolnik} M.~I. Skolnik, \emph{Introduction to Radar Systems}, 3rd ed. New York: McGraw-Hill, 2001.
\bibitem{ott} H.~W. Ott, \emph{Electromagnetic Compatibility Engineering}. Hoboken, NJ: Wiley, 2009.
\bibitem{paul} C.~R. Paul, \emph{Introduction to Electromagnetic Compatibility}, 2nd ed. Hoboken, NJ: Wiley, 2006.
\bibitem{icnirp} International Commission on Non-Ionizing Radiation Protection, ``Guidelines for limiting exposure to electromagnetic fields (100~kHz to 300~GHz),'' \emph{Health Phys.}, vol.~118, no.~5, pp.~483--524, 2020.
\bibitem{ieee521} IEEE Standard 521-2019, \emph{Standard Letter Designations for Radar-Frequency Bands}. New York: IEEE, 2019.
\bibitem{haacke} E.~M. Haacke, R.~W. Brown, M.~R. Thompson, and R. Venkatesan, \emph{Magnetic Resonance Imaging: Physical Principles and Sequence Design}. New York: Wiley, 1999.
\bibitem{nishimura} D.~G. Nishimura, \emph{Principles of Magnetic Resonance Imaging}. Stanford, CA: Stanford Univ., 2010.
\bibitem{liang} Z.-P. Liang and P.~C. Lauterbur, \emph{Principles of Magnetic Resonance Imaging: A Signal Processing Perspective}. New York: IEEE Press, 2000.
\bibitem{mispelter} J. Mispelter, M. Lupu, and A. Briguet, \emph{NMR Probeheads for Biophysical and Biomedical Experiments}, 2nd ed. London, U.K.: Imperial College Press, 2015.
\bibitem{roemer} P.~B. Roemer, W.~A. Edelstein, C.~E. Hayes, S.~P. Souza, and O.~M. Mueller, ``The NMR phased array,'' \emph{Magn. Reson. Med.}, vol.~16, no.~2, pp.~192--225, 1990.
\bibitem{iec60601} IEC 60601-2-33, \emph{Medical Electrical Equipment---Part 2-33: Particular Requirements for the Basic Safety and Essential Performance of Magnetic Resonance Equipment for Medical Diagnosis}. Geneva, Switzerland: IEC, 2015.
\end{thebibliography}
