% chapter: tb_coding (native)
\chapter{Coding, Spread Spectrum and OFDM}\label{ch:tb_coding}

\input{pedagogy/tb_coding_obj}

Getting close to the Shannon limit takes more than a good constellation: it takes
coding, and often spread-spectrum or multicarrier techniques matched to the
channel.

\section{Forward Error Correction}
FEC adds structured redundancy so the receiver can correct errors without
retransmission. Block, convolutional, turbo, and LDPC codes each buy a
\emph{coding gain} --- the reduction in required $E_b/N_0$ for a target BER ---
at the cost of overhead and decoder complexity. Modern LDPC/turbo codes approach
the Shannon limit within a fraction of a dB.

\section{Spread Spectrum}
Direct-sequence spread spectrum multiplies the data by a much faster pseudo-random
chip sequence, spreading the signal over a wide band. The receiver despreads it,
gaining a \emph{processing gain}
\[ G_p = \frac{R_{chip}}{R_{data}}, \]
which suppresses narrowband interference and enables code-division multiple
access. Frequency hopping spreads by rapidly changing carrier instead.

\section{OFDM}
Orthogonal frequency-division multiplexing splits a high-rate stream across many
narrow, orthogonal subcarriers, each seeing a nearly flat channel. A cyclic
prefix longer than the channel delay spread eliminates inter-symbol interference,
making equalization trivial --- the reason OFDM underlies Wi-Fi, LTE, and 5G. Its
cost is a high peak-to-average power ratio (PAPR) that stresses the power
amplifier.


\input{pedagogy/tb_coding}
