% chapter: tb_diodes (native)
\chapter{RF Diodes and Varactors}\label{ch:tb_diodes}

\input{pedagogy/tb_diodes_obj}

Diodes are the workhorse two-terminal nonlinear elements of RF: they detect,
mix, switch, tune, and generate harmonics.

\section{Schottky Diodes}
A Schottky (metal--semiconductor) diode has no minority-carrier storage, so it
switches extremely fast and rectifies well into the millimetre-wave range. Its
low, sharp turn-on makes it the standard device for power detectors and for
diode (passive) mixers.

\section{Varactors}
A varactor is a reverse-biased junction used as a voltage-variable capacitor,
\[ C(V) = \frac{C_0}{(1 + V/\phi)^{\,n}}, \]
with built-in potential $\phi$ and grading coefficient $n$ ($n=1/2$ abrupt,
$n\!\to\!1$ hyperabrupt). Varactors tune VCOs and filters; the useful metric is the
capacitance (tuning) ratio over the control-voltage range.

\section{PIN Diodes}
A PIN diode has an intrinsic layer that, when forward biased, stores charge and
behaves at RF as a \emph{current-controlled resistor} --- low resistance when on,
high when off --- but it does not rectify the RF because the carriers cannot
follow it. This makes the PIN diode the standard element for RF switches,
variable attenuators, and phase shifters.

\section{Other Devices}
Step-recovery diodes snap off sharply to generate rich harmonic combs (comb
generators). Tunnel and Gunn diodes exhibit negative differential resistance and
can build simple oscillators. Each exploits a specific nonlinearity of the
junction.


\input{pedagogy/tb_diodes}
