% section: tb_transistors (native)
\section{RF Transistors}\label{sec:tb_transistors}

\input{pedagogy/tb_transistors_obj}

Every active RF function --- amplification, oscillation, mixing --- rests on a
three-terminal transistor that turns a small control signal into a larger
controlled current. Choosing the right device technology is the first design
decision.

\section{Device Families}
\emph{Silicon BJT and SiGe HBT} devices offer low cost, low $1/f$ noise, and good
linearity into the tens of GHz (SiGe). \emph{CMOS} enables single-chip integration
of RF and digital, at the price of higher noise and lower breakdown. \emph{GaAs
MESFET/pHEMT} give very low noise figures and reach millimetre waves; \emph{GaN
HEMT} combines high breakdown voltage with high power density, dominating modern
power amplifiers.

\section{Figures of Merit}
The transition frequency $f_T$ is where the short-circuit current gain falls to
unity,
\[ f_T = \frac{g_m}{2\pi(C_{gs}+C_{gd})}, \]
where $g_m = \partial I_D/\partial V_{GS}$ is the transconductance. The maximum
oscillation frequency $f_{max}$, where the unilateral power gain reaches unity, is
the more relevant ceiling for amplifiers and typically exceeds $f_T$. A useful
device runs well below both.

\section{Biasing}
The transistor must be held at a quiescent operating point (bias) that sets its
$g_m$, linearity, and noise. Bias is delivered through RF chokes and bypass
capacitors that feed DC while blocking RF, and the network must itself be stable
and temperature-tolerant. Class-A bias (continuous conduction) gives the best
linearity and noise; lower conduction angles trade linearity for efficiency
(Part~V).

\section{Small-Signal Model and Technology Choice}
Near the operating point the device is described by a linear equivalent circuit
(a transconductance $g_m$, input and feedback capacitances, output conductance),
or equivalently by its measured S-parameters at that bias. Match the technology to
the job: SiGe or GaAs pHEMT for a low-noise front end, GaN for a power stage, and
CMOS when integration with baseband matters most.


\input{pedagogy/tb_transistors}
